---
title: "Valuation 2-stage firm"
subtitle: "Illumina"
params:
  # Trailing EBIT 12M
  revenues: !!r list(y4=2032, y3=2289, y2=2749, y1=2929, current=2735)
  ebits: !!r list(y4=587, y3=606, y2=883, y1=985, current=640)
  cash_flows: !!r c(1,2,3,4,5)
  ebit: 640
  rnd_current: 682
  lease_current: 73
  # If not US, add country spread
  riskless_rate: 0.0164
  risk_premium: 0.0399
  # Calculate EBIT/paid_interest; check company spread; add to riskless rate
  # Optionally add country spread
  cost_debt: 0.0233
  eff_tax: 0.233
  # Country marginal tax
  marginal_tax: 0.23
  rnd_flows: !!r list(current=682, y1=647, y2=623, y3=546, y4=504, y5=401)
  current_lease_flows: !!r list(y1=82, y2=85, y3=92, y4=91, y5=86)
  last_lease_flows: !!r list(y1=77, y2=83, y3=85, y4=86, y5=85)
  current_beyond: 488
  last_beyond: 554
  short_debt: 511
  long_debt: 1344
  equity: 4694
  goodwill: 897
  cash: 1810
  capex: 411
  depreciation: 187
  inventory: 372
  acc_recieve: 487
  acc_payable: 192
  industry_beta: 0.79
  industry_de: 0.1210
  industry_tax: 0.0416
  share_out: !!r 147
  share_price: 399
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE,
                      warning = FALSE)
```

```{r}
pacman::p_load("tidyverse", "fun.valuation")
```
#### Calculate margins
```{r}
margins <- get_margins(revenues = params$revenues,
                       ebit = params$ebits)
```

#### Calculate R&D adjustment to EBIT
```{r}
amortized_rnd <- get_amortization_3(params$rnd_flows, amortized=TRUE)
unamortized_rnd <- get_amortization_3(params$rnd_flows, amortized = FALSE)
rnd_ebit_adj <- rnd_adjustment(current_rnd = params$rnd_current, 
                               amortized_rnd = amortized_rnd)
```

#### Calculate lease adjustment to EBIT and capitalize them
```{r}
current_cap_leases <- get_leases(lease_flow = params$current_lease_flows,
                                 beyond = params$current_beyond,
                                 cost_debt = params$cost_debt)

ebit_lease_adj <- lease_adjustment(current_lease = params$lease_current,
                                   debt_value_lease = current_cap_leases$debt_value_lease,
                                   lease_embedded_years = current_cap_leases$years_embedded)

last_cap_leases <- get_leases(lease_flow = params$last_lease_flows,
                                 beyond = params$last_beyond,
                                 cost_debt = params$cost_debt)
```

#### Calculate ROIC
```{r}
roic_params <- get_roic(ebit = params$ebit,
         curr_lease_adj = ebit_lease_adj,
         rnd_adj = rnd_ebit_adj,
         eff_tax = params$eff_tax,
         short_debt = params$short_debt,
         long_debt = params$long_debt,
         equity = params$equity,
         goodwill = params$goodwill,
         cash = params$cash,
         last_lease_debt = last_cap_leases$debt_value_lease,
         rnd_asset = unamortized_rnd)
```
> Adjusted ROIC = 8%

#### Calculate Net CapEx
```{r}
net_capex <- get_net_capex(capex = params$capex,
                           depreciation = params$depreciation,
                           rnd_expense = params$rnd_current,
                           rnd_amortization = amortized_rnd,
                           lease_last_year = last_cap_leases$debt_value_lease,
                           lease_current_year = current_cap_leases$debt_value_lease)
```
> Net CapEx = 331

#### Calculate working capital
```{r}
working_capital <- get_working_cap(inventory = params$inventory,
                                   accounts_receive = params$acc_recieve,
                                   accounts_payable = params$acc_payable)
```
> Working capital = 667

#### Calculate reinvestment rate
```{r}
reinvestment_rate <- get_rr(net_capex = net_capex$net_capex,
                            working_capital = working_capital$working_capital,
                            after_tax_ebit = roic_params$after_tax_ebit)
```
> Reinvestment rate = 1.76 (176%)

#### Get growth rate
```{r}
growth_rate <- get_stable_growth(reinvestment_rate = reinvestment_rate$reinvestment_rate,
                                 roic = roic_params$adj_roic/100)
```
> Stable growth rate = 0.141 (14.1%)

#### Calculate bottom-up beta
```{r}
firm_beta <- get_beta(average_beta = params$industry_beta,
                      industry_tax = params$industry_tax,
                      average_de = params$industry_de,
                      firm_tax = params$eff_tax,
                      firm_debt = params$long_debt+params$short_debt,
                      firm_equity = params$equity)
```
> Levered beta = 1.12

#### Calculate Cost of Equity
```{r}
cost_equity <- get_cost_equity(risk_free = params$riskless_rate,
                               beta = firm_beta$levered_beta,
                               risk_premium = params$risk_premium)
```
> Cost of equity = 0.053 (5.3%)

#### Calculate Cost of Capital
```{r}
cost_capital <- get_cost_capital(marginal_tax = params$marginal_tax,
                                 cost_equity = cost_equity$cost_equity,
                                 cost_debt = params$cost_debt,
                                 equity = params$equity,
                                 debt = params$long_debt+params$short_debt+last_cap_leases$debt_value_lease)
```
> Cost of capital = 0.0406 (4.06%)

#### Get cash flows
```{r}
cash_flows <- get_cash_flow(after_tax_ebit = roic_params$after_tax_ebit,
                            reinvestment_rate = reinvestment_rate$reinvestment_rate,
                            time_period = params$cash_flows,
                            wacc = cost_capital$cost_capital,
                            growth = growth_rate$stable_growth)
```
> FCFF NPV = 2263

#### Calculate terminal value
```{r}
terminal_value <- get_terminal_value(ebit_year_five = cash_flows$ebit_year_five,
                                     stable_growth = params$riskless_rate,
                                     wacc = cost_capital$cost_capital,
                                     roic = roic_params$adj_roic/100)
```

#### Calculate Value/Share
```{r}
value_share <- get_operating_assets(npv_fcff = cash_flows$fcff_npv,
                                    terminal_value = terminal_value$terminal_value,
                                    wacc = cost_capital$cost_capital,
                                    cash = params$cash,
                                    debt = params$long_debt+params$short_debt+last_cap_leases$debt_value_lease,
                                    share_out = params$share_out,
                                    current_share_price = params$share_price)
```
> Value/Share = 217; Share price = 399






